FraCaS: Temporal Analysis

### 2020-06-09 paper2020/paper.tex
bib fixes
renumber sections

The paper is structured as follows: in \cref{sec:background}, we give
a brief summary of the frameworks whose various subsystems rely on. In
particular, the Grammatical Framework is used to construct the
syntactic parser; the Coq proof assistant checks all the reasoning; a
monad-based dynamic semantics deals with references (anaphora).  We
also provide some brief remarks on temporal semantics. In section 3,
we discuss the main aspects of the compositional semantics of our
system \textbf{This could go in the background actually}, and in
section 4, we give our main treatment of time, using various examples
from the FraCaS suite in exemplifying its effectiveness. In section 5,
we take a brief look at how our system performs with respect to the
FraCaS suite. We ran the system across the whole suite, this being the
first time that a complete run through the whole suite has been made,
but we look in particular at the performance on the temporal
section. In section 6, we conclude and discuss avenues for future
work.

@@

\section{Our Treatment of time}

@@

\section{Results and evaluation}
Our target is the FraCaS testsuite, which aims at covering a wide
range of common natural-language phenomena. The testsuite is structured in 9 sections:

@@

\section{Conclusions and Future Work}
We have presented a first attempt for a computational approach dealing
with the temporal section of the FraCaS test suite. This is the first
time a system is ran against this section, at the same time, this
concludes our work in handling the whole of the FraCaS test suite
using a combination of a number of well-studied tools: type theory,
parsing using the Grammatical Framework (GF), Monadic Dynamic
Semantics and proof assistant technology (Coq). It achieves an
accuracy of 0.71 on the Temporal Section and 0.78 overall. One of the
things to be looked at is fixing the issues associated with parts of
the test suite that ``broke'' so to say when the temporal analysis was
introduced. Some of these have been already mentioned: interaction of
the temporal variables with group readings and negation.

@@

% \bibliography{../PaperTools/bibtex/jp}

>>>>

The paper is structured as follows: in \cref{sec:background}, we give
a brief summary of the frameworks whose various subsystems rely on. In
particular, the Grammatical Framework is used to construct the
syntactic parser; the Coq proof assistant checks all the reasoning; a
monad-based dynamic semantics deals with references (anaphora).  We
also provide some brief remarks on temporal semantics. In \cref{sec:our-semantics},
we discuss the main aspects of the compositional semantics of our, using various examples
from the FraCaS suite in exemplifying its effectiveness. In \cref{sec:results},
we take a brief look at how our system performs with respect to the
FraCaS suite. We ran the system across the whole suite, this being the
first time that a complete run through the whole suite has been made,
but we look in particular at the performance on the temporal
section. In \cref{sec:conclusions}, we conclude and discuss avenues for future
work.

@@

\section{Our Treatment of time}
\label{sec:our-semantics}

@@

\section{Results and evaluation}
\label{sec:results}
Our target is the FraCaS testsuite, which aims at covering a wide
range of common natural-language phenomena. The testsuite is structured in 9 sections:

@@

\section{Conclusions and Future Work}
\label{sec:conclusion}
We have presented a first attempt for a computational approach dealing
with the temporal section of the FraCaS test suite. This is the first
time a system is ran against this section, at the same time, this
concludes our work in handling the whole of the FraCaS test suite
using a combination of a number of well-studied tools: type theory,
parsing using the Grammatical Framework (GF), Monadic Dynamic
Semantics and proof assistant technology (Coq). It achieves an
accuracy of 0.71 on the Temporal Section and 0.78 overall. One of the
things to be looked at is fixing the issues associated with parts of
the test suite that ``broke'' so to say when the temporal analysis was
introduced. Some of these have been already mentioned: interaction of
the temporal variables with group readings and negation.

@@

\bibliography{../PaperTools/bibtex/jp,paper2020}
